Proposal: Loose Grammar Inference for Lossy Compression

### 2012-10-18 proposal.tex
Crunching first paragraphs of Background

As described in the introduction, the proposed research shares many of its
goals with the \Sequitur algorithm described in \cite{sequitur}.  The authors
of \cite{sequitur} demonstrate how context free grammars offer a means of
simultaneously revealing the structure of data streams and compressing them
efficiently.  They also develop an effective algorithm based on iteratively
rewriting grammars to keep them small and efficient. \Sequitur yields
intriguing grammar based analyses of texts and musical scores, inspection of
its results finds that it unable to detect and compress larger scale structure
because of small fluctuations that occur in natural streams.  This was part of
our inspiration for trying to achieve both better compression and better
structural analysis by ignoring small scale fluctuations.

In \cite{sequitur2}, the detailed compression scheme used in the \Sequitur
algorithm is described.  By sending the grammar over in an implicit,
local-pointer based scheme, they are able to represent the grammar with very
little overhead.  A similar scheme should be easily adaptable to any grammar
based compression scheme.

>>>>

As described in the introduction, the proposed research shares many of its
goals with the \Sequitur algorithm described in \cite{sequitur}.  The authors
of \cite{sequitur} develop an effective algorithm based on iteratively
rewriting grammars to keep them small and efficient, and produce interesting
grammar-based analyses of texts and musical scores.  In \cite{sequitur2}, the
detailed compression scheme used in the \Sequitur algorithm is described.  By
sending the grammar over in an implicit, local-pointer based scheme, they are
able to represent the grammar with very little overhead.  A similar scheme
should be easily adaptable to any grammar based compression scheme.
